Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-15 paper/disc20clustering.tex
hspace
new tikz, commented

 \usepackage{balance}
 \usepackage{amsthm,amsmath,array,colortbl,graphicx,multirow}
 \usepackage{comment}
 \usepackage{balance}
 \usepackage{tikz}
 \usepackage{amsmath}
 \usetikzlibrary{patterns} %
 \usepackage{algorithm}
 \usepackage[font={footnotesize}]{subcaption}
 \usepackage[font={footnotesize}]{caption}
 \usepackage{breakcites}
 \usepackage{booktabs}
 \usepackage{diagbox}
 \usepackage{xcolor}
 \usepackage{colortbl}
 \usepackage{cleveref}
 \usepackage{enumitem}

@@

\begin{figure}[H]
	\centering
\begin{minipage}[b]{.5\textwidth}
	\hspace{15mm}
	\begin{tikzpicture}[x=0.8pt,y=0.75pt,yscale=-1.25,xscale=1.25]
	\useasboundingbox  (-3mm,-5mm) rectangle (0mm,10mm);
	%cluster 1
	\def\x{30}
	\def\w{15}
	%Shape: Rectangle
	\draw   (0,0) -- (15,0) -- (15,40) -- (0,40) -- cycle ;
	%Straight Lines
	\draw   (0,20) -- (15,20) ;
	% Text Node
	\draw (8,10) node (b1)  {$b_{1}$} ;
	% Text Node
	\draw (8,30) node (a4)   {$a_{4}$};

@@

	\draw[dotted,  shorten <= -3pt, shorten >= -5pt]  (b4) to[out=-100,in=-80] (b1);
	% arrow
	\draw[->, blue,shorten <= -3pt, shorten >= -4pt]  (b4) 
	to [out=-108,in=-130, distance=17mm]  (a4);
	\end{tikzpicture}
\end{minipage}\hfill
%
\begin{minipage}[b]{.5\textwidth}
	\begin{tikzpicture}[x=0.8pt,y=0.75pt,yscale=-1.25,xscale=1.25]
	\useasboundingbox  (0mm,-5mm) rectangle (0mm,10mm);
%cluster 1
\def\x{30}
\def\w{15}
%Shape: Rectangle
\draw   (0,0) -- (15,0) -- (15,40) -- (0,40) -- cycle ;
%Straight Lines
\draw   (0,20) -- (15,20) ;
% Text Node
\draw (8,10) node (b1)  {$b_{1}$} ;
% Text Node
\draw (8,30) node (b4)   {$b_{4}$};

@@

>>>>

 \usepackage{balance}
 \usepackage{amsthm,amsmath,array,colortbl,graphicx,multirow}
 \usepackage{comment}
 \usepackage{balance}
 \usepackage{tikz}
 \usepackage{amsmath}
 \usetikzlibrary{decorations.pathreplacing} %
 \usepackage{algorithm}
 \usepackage[font={footnotesize}]{subcaption}
 \usepackage[font={footnotesize}]{caption}
 \usepackage{breakcites}
 \usepackage{booktabs}
 \usepackage{diagbox}
 \usepackage{xcolor}
 \usepackage{colortbl}
 \usepackage{cleveref}
 \usepackage{enumitem}

@@

\begin{figure}[H]
	\centering
\begin{minipage}[b]{.55\textwidth}
	\hspace{15mm}
	\begin{tikzpicture}[x=0.8pt,y=0.75pt,yscale=-1.25,xscale=1.25]
	\useasboundingbox  (-3mm,-5mm) rectangle (0mm,10mm);
	%cluster 1
	\def\x{30}
	\def\w{15}
	%Shape: Rectangle
	\draw   (0,0) -- (15,0) -- (15,40) -- (0,40) -- cycle ;
	%Straight Lines
	\draw   (0,20) -- (15,20) ;
	% Text Node
	\draw (8,10) node (b1)  {$b_{1}$} ;
	% Text Node
	\draw (8,30) node (a4)   {$a_{4}$};

@@

	\draw[dotted,  shorten <= -3pt, shorten >= -5pt]  (b4) to[out=-100,in=-80] (b1);
	% arrow
	\draw[->, blue,shorten <= -3pt, shorten >= -4pt]  (b4) 
	to [out=-108,in=-130, distance=17mm]  (a4);
	\end{tikzpicture}
\end{minipage}\hfill
%
\begin{minipage}[b]{.45\textwidth}
	\begin{tikzpicture}[x=0.8pt,y=0.75pt,yscale=-1.25,xscale=1.25]
	\useasboundingbox  (0mm,-5mm) rectangle (0mm,10mm);
%cluster 1
\def\x{30}
\def\w{15}
%Shape: Rectangle
\draw   (0,0) -- (15,0) -- (15,40) -- (0,40) -- cycle ;
%Straight Lines
\draw   (0,20) -- (15,20) ;
% Text Node
\draw (8,10) node (b1)  {$b_{1}$} ;
% Text Node
\draw (8,30) node (b4)   {$b_{4}$};

@@

%\section{Additional Figures}
\begin{comment}
\begin{figure}[H]	\label{fig:timeline}
	\centering
\begin{tikzpicture}
\draw [->] (-10mm,0) -- (5,0);
\draw [dotted] (-13mm,0) -- (-10mm,0);

\draw [decorate,decoration={brace,amplitude=3pt}] (5mm,0.15) -- (45mm,0.15)
node [black,midway,above=1pt,xshift=1pt] {$R_{t}$};

\draw [decorate,decoration={brace,amplitude=3pt}, yshift=-18pt] (25mm,0.15) -- (-7mm,0.15)
node [black,midway,below=1pt,xshift=1pt] {$R_{t'}$};

\draw [] (45mm,2pt) -- (45mm,-2pt)
node [black,midway,below=0pt,xshift=1pt] {$t$};

% tick
\draw [] (25mm,2pt) -- (25mm,-2pt)
node [black,midway,below=0pt,xshift=1pt] {$t'$};
% tick
\draw [] (5mm,2pt) -- (5mm,-2pt)
node [black,midway,below=0pt,xshift=1pt] {$t''$};
% tick
\draw [] (-7mm,2pt) -- (-7mm,-2pt)
node [black,midway,below=0pt,xshift=1pt] {};

\draw [line width=0.33mm, red] (5mm,0) -- (25mm,0) 
node [black,midway,below=-2pt,xshift=1pt] {$\sigma_{\{u,w\}}$};

\draw [] (25mm,0) -- (45mm,0) 
node [black,midway,below=-2pt,xshift=1pt] {$\sigma_{\{u,v\}}$};

\draw [] (5mm,2pt) -- (5mm,-2pt)
node [black,midway,below=0pt,xshift=1pt] {$t''$};
%% vertical arrow 
%\draw [->] (3mm,14pt) -- (4.4mm,4pt)
%node [black,midway,above=0pt,xshift=-4pt] {separation of  $\{u,w\}$};
%% vertical arrow 
%\draw [->] (30mm,-24pt) -- (26.5mm,-7pt)
%node [black,midway,below=0pt,xshift=5pt, yshift=-5pt] {separation of  $\{u,v\}$};
\end{tikzpicture}
\caption{
Illustration of the timeline used in the proof of Theorem \ref{thm:k=2}.
Requests in $R_t$  are only to  $\{u,w\}$ and $\{u,v\}$,
which  arrive  during the interval $(t'',t]$.
Similarly,
request in $R_{t'}$  are to $\{u,w\}$ and some other pair, irrelevant to the analysis.
Hence, requests to $\{u,w\}$ are included in at most two such sets,
which are $R_{t'}$ and $R_t$.
This is because their intervals overlap on $(t'',t']$, shown with red thick line.
}
\end{figure}
\end{comment}
